---
title: "Plotting "
author: "NH"
date: "20201120"
output: pdf_document
---

```{r}
load("") # Path
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# load the package and the data
```{r}
library(brms)
library(dplyr)
E4_30P <- read.csv(file = "", header = TRUE)
E4_30P$subjectivity <- as.factor(E4_30P$subjectivity)
E4_30P$gender <- as.factor(E4_30P$gender)
E4_30P$subject <- as.character(E4_30P$subject)
E4_30P$item <- as.character(E4_30P$item)
# Sum contrast coding
contrasts(E4_30P$subjectivity) <- c(-0.5,+0.5)
contrasts(E4_30P$gender) <- c(-0.5,+0.5)
str(E4_30P)
```

## Distribution of daardoor and dus
```{r}
library(dplyr)
library(ggplot2)
library(viridis)
dfp <- E4_30P %>% group_by(subjectivity) %>% count(connective)
p <- ggplot(dfp, aes(x = subjectivity, y = n)) +
  geom_bar(
    aes(color = connective, fill = connective),
    stat = "identity", position = position_dodge(0.8),
    width = 0.3) +
  geom_text(position = position_dodge(0.8), aes(label = n, fill=connective), vjust = -0.5, size=3.5) +
  theme_classic() +
  scale_color_viridis(discrete = TRUE, option = "D", direction = -1)+
  scale_fill_viridis(discrete = TRUE, direction = -1) +
  theme(legend.position="bottom") +
  theme(legend.title = element_text(face="bold"))
print(p)

E4_30P <- E4_30P %>% filter(fluency == "flu")
```

## Distribution of daardoor and dus by participant
```{r}
# by subject
dfq <- E4_30P %>% count(subject, subjectivity, connective)
q <- ggplot(dfq, aes(x = subjectivity, y = n, color = connective)) +
  geom_bar(
    aes(color = connective, fill = connective),
    stat = "identity", position = position_dodge(0.8,preserve = "single"),
    width = 0.5
  ) +
  facet_wrap(~subject)
  
print(q)
```

## Get connective counts in the objective condition
```{r eval=FALSE}
library(tidyr)
library(dplyr)
# Get connective counts in the objective condition
dfo <- E4_30P %>% filter(subjectivity == "O")
dfo_count <- dfo %>% count(subject, connective)
dfo_count_wide <- dfo_count %>% spread(connective, n)
dfo_count_wide <- dfo_count_wide %>% rename(O_daardoor = daardoor, O_dus = dus, O_maar = maar)
# Get connective counts in the subjective condition
dfs <- E4_30P %>% filter(subjectivity == "S")
dfs_count <- dfs %>% count(subject, connective)
dfs_count_wide <- dfs_count %>% spread(connective, n)
dfs_count_wide <- dfs_count_wide %>% rename(S_daardoor = daardoor, S_dus = dus, S_maar = maar)
# combine tables
dfos_count <- bind_cols(dfo_count_wide, dfs_count_wide)
dfos_count <- select(dfos_count, -c(5))
dfos_count[is.na(dfos_count)] = 0
dfos_count <- dfos_count %>% rename(subject = subject...1)

library(ggrepel)
dfo_plot <- ggplot(dfos_count, aes(x=O_dus, y=O_daardoor)) + 
  geom_point(aes(colour = O_daardoor), size = 2) + 
  geom_text_repel(aes(colour = O_daardoor), label=dfos_count$subject, size = 3) +
  theme_classic()+
  scale_color_viridis(option = "D", direction = -1)+
  scale_fill_viridis() +
  theme(legend.position="bottom") +
  theme(legend.title = element_text(face="bold"))

print(dfo_plot)
```


## Calculate Odds ratio
### Log odds

```{r logodds.fnc}

logodds <- function( hit, miss ) {
  h <- ifelse( (hit==0|miss==0),  hit+0.5,  hit ) # add 0.5 to hit and to miss
  m <- ifelse( (hit==0|miss==0), miss+0.5, miss ) # idem
  result <- ifelse( hit==0 & miss==0, NA, log(h/m) )
  return( result )
}
```


## Odds Ratio

The following function uses the two log odds, calculated above, to compute an Odds Ratio. 
This involves some jiggling with the log transformation. 
First, we undo the log transformation of the two input parameters, then compute the odds, then do the log transformation on the result. 

```{r OR.fnc}
OR <- function( LO1, LO2 ) {
  result <- log( exp(LO1)/exp(LO2) )
  return( result ) 
}
```


```{r eda.3}
dfos_count <- mutate(dfos_count, O.logodds = logodds(O_daardoor,O_dus), S.logodds = logodds(S_daardoor,S_dus), OR = OR(O.logodds,S.logodds))
var(dfos_count$OR)
# The variance of the OR is 3.702779.

# Making the plot
logOR_plot_point <- ggplot(dfos_count, aes(x = reorder(subject, -OR), y = OR)) +
  geom_point(aes(colour = OR), stat = "identity",size = 2) +
  scale_x_discrete(guide = guide_axis(n.dodge=2))+
  theme_classic() +
  scale_color_viridis(option = "D", direction = -1) +
  scale_fill_viridis() +
  theme(legend.position="bottom") +
  theme(legend.title = element_text(face="bold"))

plot(logOR_plot_point)

# Combine tables
E4_30P <- full_join(E4_30P, dfos_count, by = "subject")
E4_30P <- select(E4_30P, -c("O_daardoor", "O_dus", "O_maar", "S_daardoor", "S_dus", "S_maar"))
```


Note that this figure is quite similar to the one above (which makes sense, see chunk `eda.1`), with the exception of the second participant, S13. 



```{r}
# Combining plots
library(patchwork)
aa <- (p|((dfo_plot + plot_layout(guides = "keep"))/logOR_plot_point)) + plot_layout(guides = "collect") & theme(legend.position = 'bottom')
aa <- aa + plot_annotation(tag_levels = "A") + plot_layout( widths = c(1,3), heights = c(1,1)) 

print(aa)
ggsave("aa.png")
```





# Building models
## 1. seg1pitchMaxst
```{r}
## m1: gender:OR:subjectivity
### SD_1
prior_E4_seg1pitchMaxst_m1.1 <- c(set_prior("normal(0,50)", class = "b", coef = "gender1"), 
                                  set_prior("normal(0,15)", class = "b", coef = "gender1:OR"),
                                  set_prior("normal(0,1)", class = "b", coef = "gender1:OR:subjectivity1"), 
                                  set_prior("normal(0,15)", class = "b", coef = "gender1:subjectivity1"),
                                  set_prior("normal(0,15)", class = "b", coef = "OR"),
                                  set_prior("normal(0,5)", class = "b", coef = "OR:subjectivity1"),
                                  set_prior("normal(0,15)", class = "b", coef = "subjectivity1"),
              set_prior("normal(0,100)", class = "Intercept"),
              set_prior("normal(0,10)", class = "sd"),
              set_prior("normal(0,10)", class = "sigma"))
E4_seg1pitchMaxst_m1.1 <- brm(seg1pitchMaxst ~ gender + OR + subjectivity + gender:OR + gender:subjectivity + OR:subjectivity + gender:OR:subjectivity + (1|subject) + (1|item),
  data = E4_30P, prior = prior_E4_seg1pitchMaxst_m1.1, family = gaussian(), warmup = 2000, iter = 10000, chains = 4, cores = 2, save_all_pars = TRUE, control = list(adapt_delta = .99, max_treedepth = 15))

### SD_3
prior_E4_seg1pitchMaxst_m1.2 <- c(set_prior("normal(0,50)", class = "b", coef = "gender1"), 
                                  set_prior("normal(0,15)", class = "b", coef = "gender1:OR"),
                                  set_prior("normal(0,3)", class = "b", coef = "gender1:OR:subjectivity1"), 
                                  set_prior("normal(0,15)", class = "b", coef = "gender1:subjectivity1"),
                                  set_prior("normal(0,15)", class = "b", coef = "OR"),
                                  set_prior("normal(0,5)", class = "b", coef = "OR:subjectivity1"),
                                  set_prior("normal(0,15)", class = "b", coef = "subjectivity1"),
              set_prior("normal(0,100)", class = "Intercept"),
              set_prior("normal(0,10)", class = "sd"),
              set_prior("normal(0,10)", class = "sigma"))
E4_seg1pitchMaxst_m1.2 <- brm(seg1pitchMaxst ~ gender + OR + subjectivity + gender:OR + gender:subjectivity + OR:subjectivity + gender:OR:subjectivity + (1|subject) + (1|item),
  data = E4_30P, prior = prior_E4_seg1pitchMaxst_m1.2, family = gaussian(), warmup = 2000, iter = 10000, chains = 4, cores = 2, save_all_pars = TRUE, control = list(adapt_delta = .99, max_treedepth = 15))

### SD_5
prior_E4_seg1pitchMaxst_m1.3 <- c(set_prior("normal(0,50)", class = "b", coef = "gender1"), 
                                  set_prior("normal(0,15)", class = "b", coef = "gender1:OR"),
                                  set_prior("normal(0,5)", class = "b", coef = "gender1:OR:subjectivity1"), 
                                  set_prior("normal(0,15)", class = "b", coef = "gender1:subjectivity1"),
                                  set_prior("normal(0,15)", class = "b", coef = "OR"),
                                  set_prior("normal(0,5)", class = "b", coef = "OR:subjectivity1"),
                                  set_prior("normal(0,15)", class = "b", coef = "subjectivity1"),
              set_prior("normal(0,100)", class = "Intercept"),
              set_prior("normal(0,10)", class = "sd"),
              set_prior("normal(0,10)", class = "sigma"))
E4_seg1pitchMaxst_m1.3 <- brm(seg1pitchMaxst ~ gender + OR + subjectivity + gender:OR + gender:subjectivity + OR:subjectivity + gender:OR:subjectivity + (1|subject) + (1|item),
  data = E4_30P, prior = prior_E4_seg1pitchMaxst_m1.3, family = gaussian(), warmup = 2000, iter = 10000, chains = 4, cores = 2, save_all_pars = TRUE, control = list(adapt_delta = .99, max_treedepth = 15))
```

```{r}
## m2: without gender:OR:subjectivity
### gender1:OR_SD_5
prior_E4_seg1pitchMaxst_m2.1 <- c(set_prior("normal(0,50)", class = "b", coef = "gender1"), 
                                  set_prior("normal(0,15)", class = "b", coef = "gender1:OR"),
                                  set_prior("normal(0,15)", class = "b", coef = "gender1:subjectivity1"),
                                  set_prior("normal(0,15)", class = "b", coef = "OR"),
                                  set_prior("normal(0,5)", class = "b", coef = "OR:subjectivity1"),
                                  set_prior("normal(0,15)", class = "b", coef = "subjectivity1"),
              set_prior("normal(0,100)", class = "Intercept"),
              set_prior("normal(0,10)", class = "sd"),
              set_prior("normal(0,10)", class = "sigma"))
E4_seg1pitchMaxst_m2.1 <- brm(seg1pitchMaxst ~ gender + OR + subjectivity + gender:OR + gender:subjectivity + OR:subjectivity + (1|subject) + (1|item),
  data = E4_30P, prior = prior_E4_seg1pitchMaxst_m2.1, family = gaussian(), warmup = 2000, iter = 10000, chains = 4, cores = 2, save_all_pars = TRUE, control = list(adapt_delta = .99, max_treedepth = 15))

```

```{r}
# Calculating Bayes factors
BF10_E4_seg1pitchMaxst_m1.1m2.1 <- bayes_factor(E4_seg1pitchMaxst_m1.1, E4_seg1pitchMaxst_m2.1)
BF10_E4_seg1pitchMaxst_m1.2m2.1 <- bayes_factor(E4_seg1pitchMaxst_m1.2, E4_seg1pitchMaxst_m2.1)
BF10_E4_seg1pitchMaxst_m1.3m2.1 <- bayes_factor(E4_seg1pitchMaxst_m1.3, E4_seg1pitchMaxst_m2.1)
# Estimated Bayes factor in favor of E4_seg1pitchMaxst_m1.1 over E4_seg1pitchMaxst_m2.1 is lower than 1. Hence, gender:OR:subjectivity is not supported. 
```


